\documentclass[a4paper]{article}
\usepackage[english]{babel}
%\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{textcomp}
\usepackage{gensymb}
\usepackage{listings}
\usepackage{color}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}

\title{Debris-Informed Underwater Search and Rescue Optimized in Two Parts}
\author{}
\date{}

\newcommand*{\Scale}[2][4]{\scalebox{#1}{$#2$}}
\pagestyle{fancy}
\fancyhf{}
\lhead{Team 40670}
\rhead{Page \thepage\, of ***}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\definecolor{black}{rgb}{0,0,0}

\renewcommand\thesection{\arabic{section}}
\renewcommand\thesubsection{\thesection.\arabic{subsection}}
\renewcommand\thesubsubsection{\thesubsection.\arabic{subsubsection}}

%\setlength\parindent{0em}
%\setlength{\parskip}{5pt}
%\renewcommand{\theenumi}{\Alph{enumi}}
\begin{document}\maketitle

\begin{abstract}
A model for optimal discrete-effort search and rescue for a plane in in water is presented. The search is split into two parts: the first is an aerial search for debris, and the second is an underwater search for the remainder of the plane body. Both of these are generalized with respect to the technology used. A current model (not included in this paper) is used to generate probability distributions for debris and the plane body in the search area. This transformation allows debris data to aid the search for a lost plane. Searches in the water are then optimized based on the likelihood of discovery versus the cost of search. Both the likelihood of discovery and cost may be changed on a per-technology basis, allowing for the simultaneous use of any number of different search technologies. Results of test runs demonstrate a logarithmic relationship between percent success, number of search vehicles, and number of searches. A direct linear relationship was found between cost of searching, number of search vehicles, and number of searches. The model does not function optimally when cost is factored in. Computation time is linear with respect to iterations and number of ships. 
\end{abstract}

\pagebreak 

\section{Introduction}

The model is partitioned into two separate searches. First, a visual aerial search is performed for floating debris. Locations and times of discovery of debris are indexed. 

An existing model for the oceanic currents of the region is presumed to already exist. This model is then applied to convert positional data of debris into a probable area of the plane crash.  This positional prediction data is combined with data from the ocean current model in order to create a more localized search area of the wreckage on the sea floor. A second underwater search, informed by the aerial search, is then conducted via underwater vehicles utilizing sonar. The underwater search maximizes search effectiveness while minimizing cost and distance of searching. 

\section{General Discrete-effort Optimal Searching}

The discrete-effort method of Lawrence Stone's \textit{Theory of Optimal Search} is used in both searches to prioritize and distribute search efforts. An overview of this method is provided here. 

\subsection{Defining the Terms Used in Searching}

The search space is divided into an integer number of ``cells'' $\mathcal{J}$. The specific technologies (i.e. one type of Autonomous Underwater Vehicle versus another) used in the search are indexed for convenience by integers in $\mathcal{T}$. This allows for implementation of different measurement accuracies and cost functions as technology advances, or simply as different technology is chosen. 

For each technology $t\in\mathcal{T}$ used, each cell $j\in\mathcal{J}$ is associated with a cost of searching. This cost is expressed in terms of the cell number and the number of times searched: $\gamma_t(j,k)$. This represents the cost of the $k$th search in cell $j$ using technology $t$.

It is important to note that $\gamma_t(j,k)$ can be defined with respect to a general cost function, $c_t(j,k)$; by contrast, $c_t$ is the cost of searching  a \textit{total} of $k$ discrete times. Ergo, $$\gamma_t(j,k_n)=c_t(j,k_n)-c_t(j,k_{n-1})$$

The probability of debris existing in a given cell is denoted by $p(j)$.

Finally, $\beta_t(j,k)$ is the probability of locating an object in cell $j$ using tech $t$ on the $k$th attempt, assuming that the object is actually in cell $j$.

The quantity $p(j)\beta(j,k)$ represents the actual chance of finding debris in the $j$th cell on the $k^{th}$ search. $\beta$ assumes the object is in the current cell being searched, where the product $\beta * p$ does not assume so.

Next, the optimization problem is stated. The optimal individual cell to focus the search methods on is the one which provides the highest chance of success per unit search cost. This value, denoted as $\epsilon$, is defined as $$\epsilon_t\equiv\epsilon_t(j,k)=\frac{p(j)\beta_t(j,k)}{\gamma_t(j,k)}$$. 

An $\epsilon$ can be computed for each cell, accounting for the number of searches $k$ for each one. The highest values are the ones with the greatest probability of success per unit cost. 

\subsection{Assigning Values to $\beta_t(j,k)$}

Suppose $\alpha_t$ is the success rate for locating surface wreckage, with technology and search aircraft as parameters. Then, from \textit{Theory of Optimal Search}: \[\beta_t(j,k)=\alpha_t\cdot(1-\alpha_t)^{k-1}\]

This representation follows that each successive search has an exponentially decreasing chance of success. The derivation is not copied here. It is worth noting, however, that the $\alpha_t$ value will significantly depend on the technology used and the context within the model is applied.

\subsection{Cost Functions as Prioritization}

The cost $\gamma(j,k)$ provides flexibility for the model in terms of prioritization. Suppose the cost per search is a constant value that is not one; then, a change of units can be easily applied in order to achieve $\gamma(j,k)=1$. In the current use of this model, the search regime simply optimizes for the highest chance of success. 

However, considerations such as distance, time, and money may be confounding variables in the cost of searching. Should these factors be disregarded, a $\gamma(j,k)=1$ will suffice. The resulting function $\gamma$ will depend entirely on the technology being used. 

For instance, one may include a distance parameter in the cost of the function, such that $\gamma(j,k)=1+d_{travel}$, where $d_{travel}$ is the distance from the current position to the position under consideration. This has the benefit of moving ships around as little as possible. One may also wish to make cost a function of time to search - in other words, $\gamma(j,k)=t_{search}+d_{travel}$. These ideas will be explored further in the later discussion on accounting for assumptions. 

\subsection{Iterating Failures}

In the event that the model does not find an object in cell $k$, the probability distribution must be modified to accommodate for the altered search area. This modification, discussed in Bayesian search theory, occurs as follows. Let $T$ represent the probability that the plane is in the cell, and $F$ the probability that it is found. Then: 
$$P(T|F)=\frac{P(T)P(F|T)}{P(F)}$$ 
$$P(T|\sim F)=\frac{p(k)[1-\beta_t(j,k)]}{(p(k)[1-\beta_t(k,j)]+(1-p(k))}$$

Thus, the posterior probability that it is there but was not found is: $$p'(k)=p(k)\frac{1-\beta_t(j,k)}{1-\beta_t(k,j)p(k)}$$.

The posterior probability of every other square can be similarly adjusted (though its proof is omitted): $$p'(k)=p(k)\frac{1}{1-p(k)\beta_t(j,k)}$$

(The notation here may be confusing. For clarification, the first $p'(k)$ adjustment applies only to the square that was searched; the second applies to every other square.)

After a failed search, the probability of the plane being in cell $k$ becomes this probability.

\subsection{Executing the Search Method}

Suppose there is a set $\mathcal{T}$ of device types and $n_t$ devices of type $t\in\mathcal{T}$. For each device, the $\epsilon$ value is computed. This represents the probability of discovering the plane in comparison to the cost of its search.

Each device is allocated sequentially to the square that is a) not already being searched, and b) has the highest $\epsilon$ value. Should two devices conflict over the optimal square, the closest device of that type claims it. Though travel time is not modeled, it is reasonable to make preliminary decisions in deference to it.

Whenever a device finishes searching, the $p$-distribution is recomputed, the device's $\epsilon$ value is recomputed based on the new distribution, and it is sent out again. 

A case where the time allowed to search is unlimited is optimal for detection. However, it is more practical that the time is limited, as would be in the case in an aerial flow model. In future applications, it would be possible to extend the aerial search model to allow for best-guessing after a constrained amount of time has expired.

\input{assumptions_file.tex}

\section{Current Flow Modeling and Aerial Search}

Existing ocean current models are sufficient for determining approximately where a discovered piece of debris could have come from. These current models are not included in this paper, although their outputs significant. and are declared as follows:

A current model is assumed to generate two probability distributions: the first is the distribution of debris, and the second is the positional distribution of the plane. The debris distribution is $p_d(j)$ (for $j\in\mathcal{J}$). The plane's positional distribution is considered naive at the outset, as it is not yet informed by the position of debris. The naive positional distribution is $p_n(j)$. 

Additionally, it is expected that the current model be able to adjust the positional probability of the plane based on the originating point of the debris. This is expressed with the operator $\mathtt{T}$. This will be defined later. 

The first step in this model for object search is to perform an aerial debris search. 

Planes will search through cells in a manner specified by the general optimal search model. The highest discovery rate to cost ratio will be investigated first, then each other cell sequentially.

The presence of debris at cell $j$ is $d_j\in \{0,1\}$. It is assumed that there either is or is not debris in a cell. If debris is present, then $\mathtt{T}$ modifies the probability distribution $p_n$ in order to represent the likelihood that debris came from a plane crash. This is expressed as: $$\mathtt{T}(d_j,p_n)=p_n'$$

Repeated application of $\mathtt{T}$ over each cell $d_j$ will create the new positional distribution informed by debris, $p_w$. This is created by: $$p_w=\mathtt{T}(d_1, \mathtt{T}(d_2, \ldots \mathtt{T}(d_j, p_n)\ldots))$$

\section{Underwater Plane Body Search}
The second step in the model is performing the underwater search. 

Autonomous underwater vehicles will follow the general search method previously stated in section 3.5. The cost function $\gamma_t(j,k)$ is slightly altered. A distance cost is added: $\gamma_t(j,k)=d$, where $d$ is the distance that would be traversed by each vessel in moving from its current location to a new target cell $k$. This cost function seeks to minimize $d$ as to overall maximize the probability of successfully locating the vessel. Analysis of the effectiveness of this function is presented in the next section.



\input{analysis_file.tex}

\pagebreak

\begin{thebibliography}{10}
\bibitem{LL} L.C.M. Lebreton, S.D. Greer, J.C. Borrero, \emph{``Numerical modelling of floating debris in the world’s oceans"}, Marine Pollution Bulletin, Volume 64, Issue 3, March 2012, Pages 653-661, ISSN 0025-326X, http://dx.doi.org/10.1016/j.marpolbul.2011.10.027.
\bibitem{Mackay98} Mackay, D.J.C, \emph{``Introduction to Monte Carlo Methods"}, submitted for publication.
\bibitem{HR} Henry R. Richardson and Lawrence D. Stone, \emph{``Operations analysis during the underwater search for Scorpion"}, submitted for publication. 
\bibitem{Stone75} Stone, Lawrence D., \textit{Theory of Optimal Search}, New York: Academic Press, 1975.
\bibitem{LS} Lawrence D. Stone, Colleen M. Keller, Thomas M. Kratzke, Johan P. Strumpfer, \emph{``Search for the Wreckage of Air France Flight AF 447"}, Statistical Science 2014, Vol. 29, No. 1, 2014.
\end{thebibliography}

\end{document}